Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-11-05 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algpseudocode}
\usepackage{algorithm, algorithmicx}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\algnewcommand\algorithmicparam{\textbf{Parameters:}}
\algnewcommand\PARAM{\item[\algorithmicparam]}
\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\INPUT{\item[\algorithmicinput]}
%\algnewcommand\STATE{\item}
\algnewcommand\RETURN{\State \textbf{Return }}

@@

\DeclareMathOperator{\DHKMSOL}{SOL}
\DeclareMathOperator{\DHKMAPP}{APP}
\DeclareMathOperator{\DHKMALG}{ALG}
\DeclareMathOperator{\DHKMERR}{ERR}
\DeclareMathOperator{\DHKMcard}{card}
\newcommand{\DHKMdataN}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^n}
\newcommand{\DHKMdataNj}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_j}}
\newcommand{\DHKMdataNjd}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
\newcommand{\DHKMERRN}{\DHKMERR\bigl(\DHKMdataN,n\bigr)}
\newcommand{\DHKMERRNj}{\DHKMERR\bigl(\DHKMdataNj,n_j\bigr)}
\newcommand{\DHKMERRNjd}{\DHKMERR\bigl(\DHKMdataNjd,n_{j^\dagger}\bigr)}
\DeclareMathOperator{\DHKMCOST}{COST}
\DeclareMathOperator{\DHKMCOMP}{COMP}
\newcommand{\DHKMhf}{\widehat{f}}
\newcommand{\DHKMhg}{\widehat{g}}
\newcommand{\DHKMtu}{\Tilde{u}}
\newcommand{\DHKMtcalK}{\widetilde{\calK}}
\newcommand{\DHKMlo}{\textup{lo}}
\newcommand{\DHKMup}{\textup{up}}
\newcommand{\DHKMinc}{\textup{in}}
\newcommand{\DHKMout}{\textup{out}}
\newcommand{\DHKME}{\textup{e}}
\newcommand{\DHKMbigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
\newcommand{\DHKMbiggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
\newcommand{\DHKMnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
%\newcommand{\normnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
\newcommand{\bignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
\newcommand{\Bignorm}[2][{}]{\ensuremath{\Bigl \lVert #2 \Bigr \rVert}_{#1}}
\newcommand{\biggnorm}[2][{}]{\ensuremath{\biggl \lVert #2 \biggr \rVert}_{#1}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
\newcommand{\YuhanNote}[1]{{\color{magenta}Yuhan: #1}}
\newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
\newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
\newcommand{\DHKMchange}[1]{{\color{red}{#1}}}

\newcommand{\tLambda}{\widetilde{\Lambda}}
\newcommand{\bcalK}{\bar{\calK}}
\newcommand{\fapp}{f_{\text{app}}}
%\newcommand{\HickernellFJ}{Hickernell}

@@

\begin{lemma} \label{DHKM:Key_Lem}
Let $\calK$ be some proper or improper subset of the index set $\bbK$. Moreover, let $\rho'$ be defined by the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau, \qquad \text{i.e., } \rho' := \frac{\rho \tau}{\rho - \tau},
\end{equation*}
so $\tau \le \rho' \le \infty$.  Let $\Lambda :=  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.  Then the following are true for $f = \sum_{\bsk \in \calK} \DHKMhf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \DHKMnorm[\calG]{\DHKMSOL(f)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK}} \le \DHKMnorm[\calF]{f} \, \Lambda,
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \DHKMbigabs{\DHKMhf(\bsk)} = \begin{cases}
    \displaystyle 
    \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}}, & \forall \bsk \in \calK, \quad  \text{if}\ \rho'<\infty, \\
    R \Lambda \delta_{\bsk,\bsk^*}, & \forall \bsk \in \calK, \ \bsk^* \in \calK \text{ satisfies } \lambda_{\bsk^*} = \Lambda, \quad\text{if}\ \rho' = \infty,
    \end{cases}
   \\ 
    \implies  \ \ \DHKMnorm[\calF]{f} = R \ \mbox{and} \ \DHKMnorm[\calG]{\DHKMSOL(f)} = R \Lambda.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} may be made tight.
\end{lemma}
\begin{proof}
We give the proof for $\rho' < \infty$.  The proof for $\rho' = \infty$ follows similarly. 
The proof of inequality \eqref{DHKM:SOL_ineq} proceeds by applying H\"older's inequality:  
\begin{align}
    \label{DHKM:SOL_A}
    \DHKMnorm[\calG]{\DHKMSOL(f)}  
    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \DHKMnorm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \biggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \DHKMnorm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{align}
Substituting the formula for $\DHKMbigabs{\DHKMhf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \DHKMnorm[\calG]{\DHKMSOL(f)}  
    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\Lambda^{\rho'/\rho}} = R \Lambda.
\end{equation*}
Moreover,
\begin{equation*}
    \DHKMnorm[\calF]{f}  
    = \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\Lambda^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof} \

Taking $\calK = \bbK$ in the lemma above, the norm of the solution operator can be expressed in terms of the norm of $\bslambda$ as follows:
\begin{equation} \label{DHKM:SOLNorm}
    \DHKMnorm[\calF \to \calG]{\DHKMSOL}  = \sup_{\DHKMnorm[\calF]{f} \le 1} \DHKMnorm[\calG]{\DHKMSOL(f)} = \bignorm[\rho']{\bslambda}.
\end{equation}
We assume throughout this chapter that the weights are chosen to keep this norm finite, namely,
\begin{equation} \label{DHKM:SOLNormFinite}
    \bignorm[\rho']{\bslambda} < \infty.
\end{equation}

@@

The optimal approximation  based on $n$ series coefficients of the input function is defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \DHKMAPP : \calF \times \N_0 \to \calG, \quad  \DHKMAPP(f,0) = 0, \ \ \DHKMAPP(f,n) := \sum_{i=1}^n \DHKMhf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
\end{equation}
By the argument leading to \eqref{DHKM:SOL_A} it follows that 
\begin{equation} \label{DHKM:APP_Err_Coef}
    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=n+1}^\infty}.
\end{equation}
An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
\begin{gather} \label{DHKM:Refined_APP_err}
    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
    \bignorm[\rho']{\bslambda^{(n+1)}}, \\
    \intertext{where the tail of $\bslambda$ is defined by}
    \label{DHKM:taillambda}
     \bslambda^{(n)} : = \bigl(  \lambda_{\bsk_i}  \bigr)_{i = n}^{\infty}.
\end{gather}
This leads to the theorem below.

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \DHKMnorm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of $\DHKMAPP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
\end{theorem}

@@

\begin{algorithm}[H]
\caption{Non-Adaptive $\DHKMALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
	\begin{algorithmic}
	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_errorBd}
	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$

@@

    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$

    \RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n^*)$
\end{algorithmic}
\end{algorithm}
We now show that this algorithm is optimal if the input set is a ball.
\begin{theorem}\label{DHKM:thm_cost_non_adapt}
The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$ that is given by
\[
\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
\]
This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
\begin{multline*}
\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') \le \DHKMCOMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
\end{multline*}
where $\varepsilon_{\max}$ and $R_{\min}$ are arbitrary and fixed, and $\omega = R_{\min}/R$.
\end{theorem}

@@

Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\DHKMhf(\bsk_1), \ldots, \DHKMhf(\bsk_{n_1})\}$. It is given by
\begin{equation} \label{DHKM:pilot_cone}
    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \DHKMnorm[\calF]{f} \le A \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\DHKMAPP(f,n)$ depends on the series coefficients not sampled.  The definition of $\calC_{\boldsymbol{\lambda},n_1,A}$ allows us to bound these as follows: 
\begin{align*}
     \MoveEqLeft{\DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
     & =  \left[ \DHKMnorm[\calF]{f}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le \DHKMERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
\end{equation}
where 
\begin{multline} \label{ErrNDef}
\DHKMERRN \\
    : =  
    \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \bignorm[\rho']{\bslambda^{(n+1)}} , 
    \\ \forall n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\calC_{\boldsymbol{\lambda},n_1,A}$, defined in \eqref{DHKM:pilot_cone}:

\begin{algorithm}
	\caption{$\DHKMALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
	\begin{algorithmic}
	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
		\INPUT a black-box function, $f$; an absolute error tolerance,
		$\varepsilon>0$

@@

\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n)$

@@

\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n_{j})$
\end{algorithmic}
\end{algorithm}

>>>>

%% Beginning of author included packages and defined macros
\usepackage{color,mathtools,bbm,xspace,natbib}
\usepackage{algpseudocode}
\usepackage{algorithm, algorithmicx}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\algnewcommand\DHKMalgorithmicparam{\textbf{Parameters:}}
\algnewcommand\DHKMPARAM{\item[\DHKMalgorithmicparam]}
\algnewcommand\DHKMalgorithmicinput{\textbf{Input:}}
\algnewcommand\DHKMINPUT{\item[\DHKMalgorithmicinput]}
\algnewcommand\DHKMRETURN{\State \textbf{Return }}

@@

\DeclareMathOperator{\DHKMSOL}{SOL}
\DeclareMathOperator{\DHKMAPP}{APP}
\DeclareMathOperator{\DHKMALG}{ALG}
\DeclareMathOperator{\DHKMERR}{ERR}
\DeclareMathOperator{\DHKMcard}{card}
\newcommand{\DHKMdataN}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^n}
\newcommand{\DHKMdataNj}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_j}}
\newcommand{\DHKMdataNjd}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
\newcommand{\DHKMERRN}{\DHKMERR\bigl(\DHKMdataN,n\bigr)}
\newcommand{\DHKMERRNj}{\DHKMERR\bigl(\DHKMdataNj,n_j\bigr)}
\newcommand{\DHKMERRNjd}{\DHKMERR\bigl(\DHKMdataNjd,n_{j^\dagger}\bigr)}
\DeclareMathOperator{\DHKMCOST}{COST}
\DeclareMathOperator{\DHKMCOMP}{COMP}
\newcommand{\DHKMhf}{\widehat{f}}
\newcommand{\DHKMhg}{\widehat{g}}
\newcommand{\DHKMtu}{\Tilde{u}}
\newcommand{\DHKMtcalK}{\widetilde{\calK}}
\newcommand{\DHKMlo}{\textup{lo}}
\newcommand{\DHKMup}{\textup{up}}
\newcommand{\DHKMinc}{\textup{in}}
\newcommand{\DHKMout}{\textup{out}}
\newcommand{\DHKME}{\textup{e}}
\newcommand{\DHKMbigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
\newcommand{\DHKMbiggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
\newcommand{\DHKMnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
\newcommand{\DHKMbignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
\newcommand{\DHKMbiggnorm}[2][{}]{\ensuremath{\biggl \lVert #2 \biggr \rVert}_{#1}}
\newcommand{\DHKMbcalK}{\bar{\calK}}
\newcommand{\DHKMfapp}{f_{\text{app}}}
\newcommand{\DHKMtLambda}{\Tilde{\Lambda}}
%\newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
%\newcommand{\YuhanNote}[1]{{\color{magenta}Yuhan: #1}}
%\newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
%\newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
%\newcommand{\DHKMchange}[1]{{\color{red}{#1}}}
%\newcommand{\HickernellFJ}{Hickernell}

@@

\begin{lemma} \label{DHKM:Key_Lem}
Let $\calK$ be some proper or improper subset of the index set $\bbK$. Moreover, let $\rho'$ be defined by the relation
\begin{equation*}
    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau, \qquad \text{i.e., } \rho' := \frac{\rho \tau}{\rho - \tau},
\end{equation*}
so $\tau \le \rho' \le \infty$.  Let $\Lambda :=  \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.  Then the following are true for $f = \sum_{\bsk \in \calK} \DHKMhf(\bsk) u_{\bsk}$:
\begin{equation}
\label{DHKM:SOL_ineq}
    \DHKMnorm[\calG]{\DHKMSOL(f)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK}} \le \DHKMnorm[\calF]{f} \, \Lambda,
    \end{equation}
    \begin{multline}
    \label{DHKM:SOL_tight_ineq}
    \DHKMbigabs{\DHKMhf(\bsk)} = \begin{cases}
    \displaystyle 
    \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}}, & \forall \bsk \in \calK, \quad  \text{if}\ \rho'<\infty, \\
    R \Lambda \delta_{\bsk,\bsk^*}, & \forall \bsk \in \calK, \ \bsk^* \in \calK \text{ satisfies } \lambda_{\bsk^*} = \Lambda, \quad\text{if}\ \rho' = \infty,
    \end{cases}
   \\ 
    \implies  \ \ \DHKMnorm[\calF]{f} = R \ \mbox{and} \ \DHKMnorm[\calG]{\DHKMSOL(f)} = R \Lambda.
    \end{multline}
Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} may be made tight.
\end{lemma}
\begin{proof}
We give the proof for $\rho' < \infty$.  The proof for $\rho' = \infty$ follows similarly. 
The proof of inequality \eqref{DHKM:SOL_ineq} proceeds by applying H\"older's inequality:  
\begin{align}
    \label{DHKM:SOL_A}
    \DHKMnorm[\calG]{\DHKMSOL(f)}  
    & = \DHKMbiggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \DHKMnorm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
    \nonumber
    & \le \DHKMbiggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \DHKMnorm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
\end{align}
Substituting the formula for $\DHKMbigabs{\DHKMhf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
\begin{equation*}
       \DHKMnorm[\calG]{\DHKMSOL(f)}  
    =  \frac{R \DHKMbignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
    = \frac{R \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
    {\Lambda^{\rho'/\rho}} = R \Lambda.
\end{equation*}
Moreover,
\begin{equation*}
    \DHKMnorm[\calF]{f}  
    = \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
    = \frac{R \DHKMbignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
    = \frac{R \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
    {\Lambda^{\rho'/\rho}} = R.
\end{equation*}
This completes the proof.
\end{proof} \

Taking $\calK = \bbK$ in the lemma above, the norm of the solution operator can be expressed in terms of the norm of $\bslambda$ as follows:
\begin{equation} \label{DHKM:SOLNorm}
    \DHKMnorm[\calF \to \calG]{\DHKMSOL}  = \sup_{\DHKMnorm[\calF]{f} \le 1} \DHKMnorm[\calG]{\DHKMSOL(f)} = \DHKMbignorm[\rho']{\bslambda}.
\end{equation}
We assume throughout this chapter that the weights are chosen to keep this norm finite, namely,
\begin{equation} \label{DHKM:SOLNormFinite}
    \DHKMbignorm[\rho']{\bslambda} < \infty.
\end{equation}

@@

The optimal approximation  based on $n$ series coefficients of the input function is defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \DHKMAPP : \calF \times \N_0 \to \calG, \quad  \DHKMAPP(f,0) = 0, \ \ \DHKMAPP(f,n) := \sum_{i=1}^n \DHKMhf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
\end{equation}
By the argument leading to \eqref{DHKM:SOL_A} it follows that 
\begin{equation} \label{DHKM:APP_Err_Coef}
    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=n+1}^\infty}.
\end{equation}
An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
\begin{gather} \label{DHKM:Refined_APP_err}
    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
    \DHKMbignorm[\rho']{\bslambda^{(n+1)}}, \\
    \intertext{where the tail of $\bslambda$ is defined by}
    \label{DHKM:taillambda}
     \bslambda^{(n)} : = \bigl(  \lambda_{\bsk_i}  \bigr)_{i = n}^{\infty}.
\end{gather}
This leads to the theorem below.

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \DHKMnorm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \DHKMbignorm[\rho']{\bslambda^{(n+1)}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of $\DHKMAPP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
\end{theorem}

@@

\begin{algorithm}[H]
\caption{Non-Adaptive $\DHKMALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
	\begin{algorithmic}
	\DHKMPARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_errorBd}
	\DHKMINPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$

@@

    \State Choose $n^* =  \min \left \{n \in \N_0 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$

    \DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n^*)$
\end{algorithmic}
\end{algorithm}
We now show that this algorithm is optimal if the input set is a ball.
\begin{theorem}\label{DHKM:thm_cost_non_adapt}
The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$ that is given by
\[
\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
\]
This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
\begin{multline*}
\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') \le \DHKMCOMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
\end{multline*}
where $\varepsilon_{\max}$ and $R_{\min}$ are arbitrary and fixed, and $\omega = R_{\min}/R$.
\end{theorem}

@@

Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\DHKMhf(\bsk_1), \ldots, \DHKMhf(\bsk_{n_1})\}$. It is given by
\begin{equation} \label{DHKM:pilot_cone}
    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \DHKMnorm[\calF]{f} \le A \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\DHKMAPP(f,n)$ depends on the series coefficients not sampled.  The definition of $\calC_{\boldsymbol{\lambda},n_1,A}$ allows us to bound these as follows: 
\begin{align*}
     \MoveEqLeft{\DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
     & =  \left[ \DHKMnorm[\calF]{f}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le \DHKMERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
\end{equation}
where 
\begin{multline} \label{ErrNDef}
\DHKMERRN \\
    : =  
    \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \DHKMbignorm[\rho']{\bslambda^{(n+1)}} , 
    \\ \forall n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\DHKMbignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\calC_{\boldsymbol{\lambda},n_1,A}$, defined in \eqref{DHKM:pilot_cone}:

\begin{algorithm}[H]
	\caption{$\DHKMALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
	\begin{algorithmic}
	\DHKMPARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
		\DHKMINPUT a black-box function, $f$; an absolute error tolerance,
		$\varepsilon>0$

@@

\DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n)$

@@

\DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n_{j})$
\end{algorithmic}
\end{algorithm}
